---
title: "Top Hat BoxPlots"
author: "Dr. Cannata"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

Here's what's loaded:  
library(tidyverse)  
library(shiny)  
library(grid)  
library(data.world)  
library(DT)  
library(shinydashboard)  
library(plotly)  
library(lubridate)  

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#data.world Project and GitHub Links
A link for your data.world Project should go in this Section.

A link for your GitHub Classroom Repository should go in this Section.

#data.world "Insight" Links
Here's how to insert a data.world "Insight" link.  
Click on the data.world "Insight", copy the URL and insert it like this:  
[Insight](https://data.world/cannata/tophatsuperstoreproject/insights?anchor=https%3A%2F%2Fwww.filepicker.io%2Fapi%2Ffile%2FBlTI0Rn7SJK7wsyxDBuE&id=787cd1d7-a480-453e-ab35-3e06b6c43461&source=sb)

**"Insight" should be spread throughout the document as appropriate.**

#Tableau Workbook Links
R supports embedded iFrames in its Interactive Documents, and Tableau supports embedding its fully functional tables in iFrames, so this can be used to embed Tableau graphs in Interactive Documents.
In order to do this, the iframe tag must be included in the .Rmd file outside of a code block, i.e.,

<iframe src="https://public.tableau.com/views/TopHatBoxplots/SalesBoxplots?:showVizHome=no" width="800" height="500"></iframe>

The src url above can be obtained by

* signing into [Tableau Public](https://public.tableau.com/en-us/s/)
* viewing on the desired workbook
* click on the "Share" icon at the bottom right
* copy the URL from the "Link" box (not the Embed Code box)

After you get this URL, you need to strip all existing URL parameters and replace them with this one:
 
" ?:showVizHome=no "  
This should embed the Tableau graph in an iFrame whose size can be edited within the iFrame tag. I hope this will prove useful.

Note - the embedded Tableau will only show up in an actual browser window, it will not show up in a preview window. 

#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("DataA.R", local = TRUE)
source("DataB.R", local = TRUE)
```
**Each new query should be in its own DataN.R file**  
As an example, here's the code that is in the DataA.R file:  
dfA <- eventReactive(c(input$selectRegion_1, input$salesFilter_1), {   
  project <- "https://data.world/cannata/tophatsuperstore"   
  data.world::set_config(cfg_env("DW_API"))   
  paramQuery <- data.world::qry_sql(  
    "   
    select region, category, sales  
    from superstore s  
    where sales between ? and ? and region in (?, ?, ?, ?)  
    order by region  
    ")  
  paramQuery$params <- c(input$salesFilter_1[1], input$salesFilter_1[2],   input$selectRegion_1[1], input$selectRegion_1[2], input$selectRegion_1[3],   input$selectRegion_1[4])  
  data.world::query(paramQuery, dataset = project)  
})  

dfA1 <- eventReactive(c(input$selectRegion_1, input$salesFilter_1, input$yDataMin__1_,   input$yDataMax__1_), {   
  if( ! is.na(input$yDataMin__1_) & ! is.na(input$yDataMax__1_)) {  
    dfA() %>% dplyr::filter(between(sales, input$yDataMin__1_, input$yDataMax__1_))  
  }  
  else {  
    dfA()  
  }  
})  

#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/cannata/tophatsuperstore" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from superstore 
 "), 
dataset = project)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Regions <- eventReactive(c(input$selectRegion_1), { 
  library('stringr')
  str_c(input$selectRegion_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting regions (notice - choices is set to the regions variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("East", "West", "Central", "South")),
  sliderInput("salesFilter_1", label = "Sales:", min = 0, max = 100200, value = c(0, 100200), step = 100)
)
```

#Render and Display the BoxPlots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Category Sales BoxPlot", tabName = "boxplot1", icon = icon("dashboard")),
      menuItem("Quarter Sales BoxPlot", tabName = "boxplot2", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Category Sales BoxPlot" tab content
      tabItem(tabName = "boxplot1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("BoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Quarter Sales BoxPlot" tab content
      tabItem(tabName = "boxplot2",
        p("And here."),
        source("BoxPlot2UI.R",local = TRUE)$value
      )
    )
  )
)
source("BoxPlot1Server.R", local = TRUE)
source("BoxPlot2Server.R", local = TRUE)
```
###As an example, here's sample code from BoxPlot2UI.R  
 # Change "Histogram", all __1_s, and edit tiles below:  
tabItem(tabName = "Histogram",  
        tabsetPanel(   
          tabPanel("Plots"),# To create a tab panel - see https://shiny.rstudio.com/reference/shiny/latest/tabPanel.html  
          tabPanel("Data",   
             dataTableOutput('table__1_'),  
             downloadButton('download__1_',"Download the data")),  
          tabPanel("Plot Size",   
             numericInput("plotWidth__1_", "Plot Width (Required)", 1000),  
             numericInput("plotHeight__1_", "Plot Height (Required)", NA)),  
          tabPanel("Plot Title",  
             textInput("title__1_", "Title 1", "Region Shipping Costs"),  
             numericInput("titleFont__1_", "Title Font", 10)),   
          tabPanel("Plot Legend",  
             textInput("legendTitle__1_", "Legend Title", "Regions"),  
             numericInput("legendTitleSize__1_", "Legend Title Size", 10),  
             numericInput("legendItemSize__1_", "Legend Item Size", 10),  
             numericInput("legendKeySize__1_", "Legend Key Size", 5)),   
          tabPanel("Axis Labels",  
             textInput("xLabel__1_", "x-Axis Label", "Shipping Costs"),  
             textInput("yLabel__1_", "y-Axis Label 1", "Shipping Costs Count"),  
             numericInput("textFont__1_", "textFont", 10)),  
          tabPanel("Data Size",   
             numericInput("yDataMin__1_", "yData Minimum (Required)", 0),  
             numericInput("yDataMax__1_", "yData Maximum (Required)", NA))),  
        plotlyOutput("Histogram__1_", height=800)  
)  


###As an example, here's sample code from BoxPlot1Server.R  
 # Change all __1_s, Download information, and edit the plot and ggplotly arguments below:  
 # Build Download Button and Output DataTable---------------  
  output$download__1_ <- downloadHandler(  
    filename = function(){"CategoryBoxplot.csv"},   
    content = function(fname){  
      write.csv(dfA1(), fname)  
    }  
  )  
  output$table__1_ <- renderDataTable({  
    DT::datatable(dfA1() , rownames = FALSE, extensions = list(Responsive = TRUE,   FixedHeader = TRUE)  
    )  
  })  
# ---------------------------------------------------------  
# Build and Output Throughput Plot ------------------------  
  output$Histogram__1_ <- renderPlotly({  
    plot = dfA1() %>% ggplot() +   
      geom_boxplot(mapping = aes(x = category, y=sales, colour = region)) +  
      
      theme_bw() +  
      theme(plot.title = element_text(size = input$titleFont__1_, face = "bold")) +   
      theme( # Legend Attributes - see https://github.com/tidyverse/ggplot2/wiki/Legend-Attributes  
        legend.title=element_text(size=input$legendTitleSize__1_),  
        legend.text=element_text(size=input$legendItemSize__1_),  
        legend.key = element_rect(size = input$legendKeySize__1_),  
        legend.key.size = unit(input$legendKeySize__1_, 'lines')) +  
      theme(axis.text=element_text(size=input$textFont__1_),  
            axis.title=element_text(size=input$textFont__1_, face="bold"),  
            axis.text.x = element_text(angle = 45, hjust = 1))  +  
      theme(plot.margin=unit(c(2,2,2,2),"cm")) +  
      scale_y_continuous(labels = scales::comma) + # Disable scientific notation  
      ggtitle(paste(Regions(), input$title__1_)) +  
      xlab(input$xLabel__1_) + ylab(input$yLabel__1_) +  
      theme(axis.title.y = element_text(margin = margin(t = 10, r = 10, b = 10, l = 10))) +  
      scale_color_discrete(name = input$legendTitle__1_)  
    
    if( ! is.na(input$plotWidth__1_) & ! is.na(input$plotHeight__1_))  
     ggplotly(plot, tooltip = c("sales"), session="knitr", width = input$plotWidth__1_, height = input$plotHeight__1_)  
    else
      ggplotly(plot, tooltip = c("sales"), session="knitr")   
  })  
# ---------------------------------------------------------


#Essential steps to add a new plot to a Dashboard:  
##1. Copy and change "boxplot1" to "boxplot2" as in bold below:  
  dashboardSidebar(  
    sidebarMenu(  
      menuItem("Category Sales BoxPlot", tabName = "boxplot1", icon = icon("dashboard")),  
**menuItem("Quarter Sales BoxPlot", tabName = "boxplot2", icon = icon("dashboard"))**    
       
##2. Copy and make changes in three places as shown in bold below below:  
dashboardBody(  
    tabItems(  
      # 1. "Category Sales BoxPlot" tab content  
      tabItem(tabName = "boxplot1",  
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),  
        source("BoxPlot1UI.R",local = TRUE)$value  
      ),  
      
**# 2. "Quarter Sales BoxPlot" tab content**  
**tabItem(tabName = "boxplot2",**  
p("And here."),  
**source("BoxPlot2UI.R",local = TRUE)$value**  
      )  
    )  
  )  
  
##3. Add Server.R file as shown in bold below:  
  source("BoxPlot1Server.R", local = TRUE)  
  source("BoxPlot2Server.R", local = TRUE)  
  
##4. Open a BoxPlot1UI.R file, save as a new BoxPlot2UI.R file, and change __N_ to __M_  

##5. Open a BoxPlot1Server.R file, save as a new BoxPlot2Server.R file, and change __N_ to __M_  

# Make a Second Dashboard  
##1. Copy and Paste the Dashboards chunk above.  
##2. Remove all but on sidebarMenu item.  
##3. Rename the source files to new source files as in Steps 2 and 3 above.  
##4. Create the new UI.R and Server.R files as in Steps 4 and 5 above.  
##5. Add more sidebarMenu items as outlined above.  

#Appendix

##Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

##Data Cleaning Code.
To be addressed in the next Chapter.
